At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-11-30 manuscript/reply_to_referees_2.tex

			(related with this part of the methods but referring to the Introduction section) Which are the hypothesis for this analysis? How do you think that family composition (and no species composition) could affect the relationship between phylogenetic  distances and niche overlap?
			In the analysis it is not clear for us which are the dependent and independent variables. Is the independent variable a matrix with coefficients of similarity between networks?  Do you want to explore if more similar networks have a more similar relationship (slope) between phylogenetic distance and niche overlap? Or you want to investigate if the slopes are more o less strong depending on the local composition of communities (for each network separately) ? If this is the case you could compare slopes with a local diversity index (e.g. Shannon) instead of a beta diversity index.
		\end{refquote}

		\textbf{R:} The Referee was correct with their first idea. We want to explore whether more similar networks have more similar slopes of partner overlap against phylogenetic distance. Once again, we are pleased that the Referee agrees with our analysis. We did this because different plant families likely experienced different levels of convergence, coevolution, have different levels of intimacy with their partners, etc. We now explicitly state this in the introduction. Note that we cannot use Shannon diversity within networks as we do not know the abundances of the various plant species. All we can do is test the effect of numbers of species as described above.

@@

		\begin{quotation}

			Here we investigate how overlap in interaction partners between 
			pairs of plants (henceforth ``niche overlap'') varies over 
			phylogenetic distance. 
			Whereas previous 
			studies have focused on the presence or absence of phylogenetic
			signal across entire networks, we take a pairwise perspective in
			order to obtain a more detailed picture of how plant phylogeny
			relates to network structure. As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network. 
			This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.

  		\end{quotation}

	16. Critique of manuscript structure

		\begin{refquote}
			Results\\
			General: Please, do not include discussion in your results, it may confound readers.
		\end{refquote}

		\textbf{R:} We are unsure whether the Referee is giving general advice here or if there is a specific element of the results the Referee feels would fit better in the discussion. We thank the Referee for the advice but can take little practical action without more details as to the nature of their objection.

	17. Incorrect claim that beginning of results is inaccurate

@@

		\begin{refquote}
			Line 262. Your first sentence of results do not correspond with what follows. We will suggest you use most networks, or most herbivory networks and half pollination networks, or using the percentages you present in the discussion section.
		\end{refquote}

		\textbf{R:} This comment's somewhat eccentric grammar makes it rather difficult to parse. We are guessing that the Referee is confused by the overall trend (more related plants have more similar interaction partners) and the variability of the trends within specific networks. To help understand this, note that the structure of the first few lines of the discussion parallel the first few lines of the results. First we introduce the overall result, and then we expand upon the details. We have lightly edited lines 370-373 to make this clearer:

			We found general support for the hypothesis that more
			closely-related pairs of plants have a higher degree
			of niche overlap. Taking all networks together, 
			the probability of two plants sharing the same animal 
			interaction partners decreased with increasing 
			phylogenetic distance. Considering networks separately ...

	18. Definition of community composition unclear

@@

		\begin{quotation}
			Next, we examined the connection between our network-level observations
			and the number of species in each plant family present in each community.
			Specifically, we tested the hypothesis that
			varying relationships between phylogenetic distance and
			niche overlap are due to the different distributions 
			of families across networks. We defined the relationship between
			phylogenetic distance and niche overlap as the change in 
			log odds of two plants in a given network sharing an interaction 
			partner per million years of divergence (i.e., the slope $\beta_{distance}$ from the 
			regression of niche overlap against phylogenetic distance within
			a single network). We then related differences in this relationship
			to differences in the composition of the plant community 
			using a non-parametric permutational multi-variate 
			analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
	    \end{quotation}

	19. Confusion about permutation methodology

		\begin{refquote}
			Minor comments on Results
			297-298 You permuted interactions or phylogenetic distances?
		\end{refquote}

		\textbf{R:} As stated in the methods, we permuted interactions. Note that, in statistical terms, the two approaches are equivalent, but we appreciate that this may not be clear to readers unfamiliar with permutation approaches. We have rephrased the results to match the methods.

	20. Typo in Fig. 1 caption

@@

		\textbf{R:} As the caption states, the minimum and maximum slopes were always very close to 0. We therefore had to choose between a y-axis scale which would show the observed slopes or one which would show the differences in slopes for the permutations. As the observed slopes are far more important than knowing the exact values of the permutation slopes, we chose to prioritise the former.

	22. Confusion about line 328

		\begin{refquote}
			Line  328: "...increasing phylogenetic distance in 12...", what is 12? the number of families?
		\end{refquote}

		\textbf{R:} Yes, 12 is the number of families. We have revised the line to make this more explicit. Note that we have also corrected this line to match Table 1, which includes 14 significant families.

@@

		\textbf{R:} We have reordered the tables and added a redundant reference to Fig. 3.

	24. Suggestion to include ideas about evolution and coevolution

		\begin{refquote}
			Discussion
			General
			We suggest you include ideas about evolution and coevolution in networks in your discussion. It is important to recognize that network structure is in part a consequence of the evolutionary process and that we cannot think in the pairwise-coevolutionary framework as the only one modulating trait evolution in species rich assemblages.
			You state that the fact that the proportion of specialist species may explain differences between plant-pollination and plant-herbivore network patterns and you discuss the mathematical consequences of such difference but you should discuss the ecological and evolutionary causes and consequences of having higher specialization in pollination networks. This is also related with your methodological decision of excluding more specialized herbivores, isn't it?
		\end{refquote}

		\textbf{R:} We do include ideas about evolution and coevolution in our discussion. We completely agree that, together with ecological processes and environmental filtering, evolution and coevolution are very important in structuring networks at every level, from pairs of species to entire communities. However, since we do not have trait or genetic data for our networks, we cannot comment with any certainty on which of our results are due to trait plasticity or environmental influence and which are due to evolution. We therefore mention possible evolutionary and ecological explanations together.

@@

		\end{quotation}

	25. Objection to the word "broad"

		\begin{refquote}
			338-339. You state We found broad support for the hypothesis that more closely-related pairs of plants have a higher degree of niche overlap. This is a very strong sentence that is not supported by your results. You found evidence in 55\% of plant-pollination networks (almost half of your dataset). In fact, it is interesting to note that even the slope is more pronounced in mutualistic networks you found higher support in herbivory networks, as a higher percentage of networks showed a tendency.
		\end{refquote}

		\textbf{R:} Note that 56\% is greater than half, and that when all networks were considered together we also observed the same trends. We contend that these two facts do represent broad support for our hypothesis and note that the Hembry et al reference suggested by the Referee uses the word in a very similar way. Broad support is not, of course, universal support. That is why we provide the numbers of networks. Readers are thereby armed with the tools to agree or disagree with our choice of words. In case it is the synonymy between broad and general that has perplexed the Referee, we have changed this line to state ''We found \emph{general} support...''. We hope that this is clearer.

		We are glad that the Referee finds the greater proportion of significant herbivory networks interesting. With the unbalanced sample sizes of pollination and herbivory networks, however, we are somewhat reluctant to make much of the difference between 56\% and 64\%. We consider that the important point here is that networks are more likely than not to show decreasing niche overlap with increasing phylogenetic distance.

	26. Confusing complaint about subsetting herbivory networks or perhaps objection to the claim that oligotrophy is common

@@

		\begin{refquote}
			351-352 The herbivory networks did not contain as many obligate specialists, but we note that many herbivorous insects are oligotrophs which consume only a few closely-related hosts (Novotny \& Basset, 2005; Yguel et al., 2011). This sentence is confuse because you have a subsample of herbivory networks and then this seems to be a by-product of your study design associated with your decision of removing networks that may show strong phylogenetic signal.
		\end{refquote}

		\textbf{R:} We must again point out that subsetting the herbivory networks as we have done was requested during an earlier round of review. We are therefore reluctant to reconsider this approach without a very good reason.

		Beyond that, it is very difficult to work out exactly what the Referee objects to in this sentence. If the Referee is objecting to our references, note that~\citet{Novotny2005} addresses leaf-chewers as intermediate in their level of specialisation on particular families and emphasises that herbivores in general (regardless of guild) tend to consume a few closely-related hosts. They point out the relative rarity of strict specialists compared to specialists on species within a particular genus or family.~\citet{Brandle2006} also found insect herbivores were specialised on a particular genus but consumed multiple species within the genus. As~\citet{Brandle2006} focus on phytophagous insects specifically, we feel that this reference addresses our point more directly than~\citet{Yguel2011}. We have therefore replaced this reference. We hope that this improved selection of references will help the Referee's confusion.

		If the Referee objects to our finding that the herbivores in our networks tended to consume more than one plant species, there is little we can do about it. That is simply what our data say.

		If the Referee is contending that, because of the multiple herbivore types in~\citet{Novotny2005}, we cannot claim that the herbivores in our dataset are oligotrophs, we can respond with further details. The mean number of plants consumed per herbivore ranged between 1.64 and 14.9 across networks, with a mean of 6.36, and the median ranged between 1 and 11.5 (mean 4.68). These measures indicate that many herbivores in our networks do, in fact, consume only a few of the plants available to them (with some highly generalist species increasing the means). Our overall point, that oligotrophy may be common in herbivores, therefore stands.

	27. Claims that congeneric species are not closely related

@@

		\begin{refquote}
			357-359 This suggests that conservation of interaction partners among closely related plants (e.g., congeners or members of the same subfamilies) is more important than phylogenetic signal from deeper within the phylogenetic tree. Congeneric species can be not closely related, please revise sentences like this one across the manuscript because you are confounding phylogeny with taxonomy.
		\end{refquote}

		\textbf{R:} Does the Referee really mean to suggest that plants in the same genus are generally less closely-related than plants in different families? Without some sources to substantiate this, we find this claim very counter-intuitive. This is especially surprising given the Referee's insistence that we should expect similar interaction partners within a family. We agree that taxonomy is only a proxy for phylogeny, but we are not aware of any evidence that it is a poor proxy. We also note A) that similar language is quite common in the literature and B) that across seven other reviews, no other Referee has suggested that species in the same taxonomic groups (e.g., genera) are less closely-related than species in different groups. Without any evidence to support this claim, we have opted not to change our text.

@@

	28. Another demand to discuss intimacy [[done. Look for more places to scattershot Hembry]]

		\begin{refquote}
			361-365. How interaction intimacy may explain your results? Please, discuss your results in light of the interplay between interaction type (pollination, herbivory) and intimacy (see Hembry et al. 2018).
		\end{refquote}

		\textbf{R:} We do not believe that interaction intimacy has a strong effect on our results, as both leaf-chewing herbivory and pollination are low-intimacy interactions~\citep{Astegiano2017}. It is possible that there is variation in intimacy within these broad categories, but we do not have data that would allow us to test such a hypothesis. We also note that~\citet{Hembry2018} study a very small and high-intimacy system (a single genus of brood pollinating moths and their single genus of host plants). Their results will therefore not necessarily generalize to the larger, more diverse networks we consider. Indeed, had they considered a broader sample of plants and seed predators or herbivores from the same islands, they easily could have found less reciprocal specialisation. As a detailed study of this unusual mutualism was the aim in~\citet{Hembry2018} this is not a problem for their work, but we are hesitant to infer too strong a relationship between their findings and ours.

		This reference suggestion is also somewhat confusing as~\citet{Hembry2018} did not find evidence for host-associated differentiation in their moths. This would seem to undermine the idea that evolution/coevolution can explain network structure. Moreover, they point out that the support for the intimacy hypothesis  in their system was broad (in the same sense we used the word) but equivocal. This exacerbates the difficulty of extrapolating their work to explain our results.

		Given all of the above, it is hard to see how the interaction intimacy hypothesis relates to these lines (which are about whether the number of species in different plant families is related to the strength of phylogenetic signal). Instead, we feel that a discussion of the possible effects of intimacy is more relevant later on, where we discuss possible reasons why some families may show different trends. This section (lines 443-454) now reads:

@@

			Indeed, animal pollination and seed dispersal have been shown to act
			as filters for several plant clades~\citep{Mayfield2009}. Selection to avoid 
			competition and restrict numbers of interaction partners may lead to
			more intimate or specialised interactions~\citep{Ponisio2017}. 
			Reciprocal specialisation is particularly expected in highly intimate interactions~\citep{Hembry2018} rather than the relatively low-intimacy pollination or leaf-chewing herbivory we consider here~\citep{Astegiano2017}.
			Despite this, it is still possible that some plant families may tend to have more intimate interactions than others. This could result, for example, if a plant is pollinated by an insect which is also a herbivore in its larval stage~\citep{Hembry2018}. 
			Whether or not intimacy plays a role in structuring these interactions, past selection to avoid competition is 
			consistent with the relatively high proportion of extreme specialists we
			observed in the pollination networks.

		\end{quotation}

\clearpage

{\Large \bf Reply to Referee 3}

	\begin{refquote}
		The study is well designed and the manuscript well written, and the authors clearly demonstrate their comprehensive grasp of the subject and the applied statistical analyses.
		My only more general comment is whether authors have considered potential applications of such phylogenetic approaches for ecological restoration? If closely-related species provide similar functions in ecological networks, they could be used interchangeably to restore ecological interactions/functions. This is an exciting potential application of phylogenetic data in biodiversity conservation and restoration, and could be touched upon/discussed in this manuscript.
		Otherwise, I have only minor comments.
	\end{refquote}

@@

		\textbf{R:} We have changed the title to state our main result while also pointing out some of the important variability between networks. We do feel that this variability is a major feature of our results, as well as previous studies of phylogenetic signal across systems, and it is too easy to forget if not emphasized. We hope that the Referee will agree that our new title, "Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families", strikes a balance between these two considerations.

		% "At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families.”

		% - suggests that we focus on broad support. Maybe "Broad conservation of pollinators and herbivores in a global dataset"?
		% "Despite variation among families, pollinators and herbivores are broadly conserved among related plants"?
		% "Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families"?

	2. Request to state that networks are qualitative rather than quantitative

@@

    	\begin{quotation}

		  Although here we considered only the presence or absence of interactions,
		  (i.e., qualitative networks) ...

    	\end{quotation}

	3. L298 – Please be careful with use of “lesser/greater” “more negative or positive than expected from permuted networks”

@@

\clearpage

{\Large \bf Reply to Referee 4}

	\begin{refquote}
		Understanding what drives the structure of networks of interactions is key to predict the structure of plant-insect communities (e.g., for conservation or restoration purposes, or to support benefit organisms in agriculture).
		The present study focuses on the contribution of the evolutionary history to the interaction structure, and makes a significant contribution to the understanding of the variability of the phylogenetic signal in plant-insect networks. Here, the strength of the phylogenetic signal is actually quantified while it usually relies on correlation scores, and the effect of plant composition and the identity of plant families are examined to assess whether they could explain the variability of trends described in the literature.
		The dense writing turns out to be a double-edge sword: a lot of information on drivers of phylogenetic signals is compiled in here, but the text is sometime hard to follow. Hence, my following comments mostly pertains to the form, and I trust the authors should be able to address them fairly easily.
	\end{refquote}

	\textbf{R:} We thank the Referee for their compliments to our analysis and for taking the time to review our manuscript so thoroughly. We acknowledge that our writing can be dense at times and appreciate the Referee pointing out places where we may clarify our prose. We especially appreciate the detailed suggestions for how to improve our second-to-last paragraph, and have followed them to the best of our ability. Below, we respond to each comment in detail (preceded by \textbf{R:}). We are confident that revising the manuscript in response to the Referee's comments has significantly improved it.

	1. Confusion about description of tuple-form dependent variable

		\begin{refquote}
			* Modelling the relationship between niche overlap and phylogenetic distance\\
			I did not managed to fully grasp the statistical analysis right away (I reckon I'm not a statistical master, but this may be the case of other readers), and I think it was mostly due to the way the methods are described. The writing is nice, but some tiny details are missing while they could help the reader to understand more quickly how the authors distinguish the use of the {M\_ij, U\_ij}-tuple from that of J\_ij.
			Based on l. 143-167, I understand that the number of shared interactions M\_ij is modelled with a binomial distribution, with the number of trials being M\_ij+U\_ij, and the probability of success being w\_ij (M\_ij ~ B(M\_ij + U\_ij, w\_ij)). The {M\_ij, U\_ij}-tuple would appear in R as follows:
			model $\leftarrow$ glm(cbind(M\_ij, M\_ij+U\_ij) \~ d\_ij + ..., family = “binomial”)
			But, can we actually say that there are two dependent variables? To me, it is the number of shared interactions that is modelled as a binomial process, not both the number of shared and unshared interactions.

@@

			\smallskip

			p. 5, l. 69-71 « In either case, dissimilarity (…). » This sentence helped me to understand why it is important to look at unshared interactions. To be better showcased ?

		\end{refquote}

		\textbf{R:} The number of shared and unshared interactions are indeed both dependent variables included in the analysis. The number of shared variables is the key variable, but the number of unshared interactions is also important as it indicates how extraordinary a particular number of shared interactions is. The binomial process incorporates both quantities; converting the numbers of shared and unshared interactions to a proportion and weighting the observations by the total number of interactions. We thank the Referee for pointing out text in the introduction which clarified the purpose of including unshared interactions, and have used it as the basis for improving the methods. We have expanded the beginning of this section to explain the logic of our modelling approach in more detail.

@@

			We calculated niche overlap for each pair of plants $i$ and $j$ based on the number of shared and unshared interaction partners ($M_{ij}$, $U_{ij}$, respectively). 
			The number of unshared interaction 
			partners gives valuable information about cases where, for example, 
			closely-related plants may have experienced disruptive selection, leading to weaker phylogenetic signal. 
			The sum $M_{ij} + U_{ij}$ indicates the amount of information  provided by each pair of plants: a pair of generalists which share most of their interaction partners gives a stronger indication of phylogenetic signal than a pair of extreme specialists with one common interaction partner.

### 2019-11-30 manuscript/reply_to_referees_2.tex

			Together, $M_{ij}$ and $U_{ij}$ give a Jaccard index ($J_{ij}$) describing 
			the proportion of shared interactions. $J_{ij}$ is defined: 
			\begin{equation}
			J_{ij} = \frac{M_{ij}}{U_{ij}+M_{ij}} ,
			\end{equation}
			where $M_{ij}$ is the set of \emph{mutual} (shared) interaction partners and $U_{ij}$ the set of unshared interaction partners for plants $i$ and $j$.

		\end{quotation}

	2. Request to state that we use the Jaccard index more explicitly

@@

	3. Request to make non-independence of species within each community explicit.

		\begin{refquote}
			Another point pertains to the definition of “trials” in the binomial-distributed process. If I get it right, these correspond to the union of species i and j interactions (of size P\_i + P\_j -2M\_ij = M\_ij + U\_ij). However, these are not independent for reasons highlighted in the introduction (e.g., competition, facilitation between plants and/or insects). This may question the robustness of the analysis, but testing the effect of the plant community composition (negative) allows to verify this. This should be specified, I think.
		\end{refquote}

		\textbf{R:} We actually address the non-independence of trials (pairs of plants) by calculating $p$-values based on permutations of the observed networks (as opposed to assuming independent, binomially-distributed trials, which is certainly not the case). To emphasize our explanation of this, we have reordered the text and placed our discussion of the permutation methods under the sub-heading 'accounting for non-independence'. We hope that this will calm reader's worries about the validity of our conclusions.

	4. Permuting the permuted networks is confusing

		\begin{refquote}
			* Evaluating type I and type II errors: Permutations of permutations\\
			Paragraph p. 10, l. 187-197 is a bit confusing because of phrasings such as “permutations/permuting of the permuted networks”. I don't have a better way to name this second round of permutations, but the overall is difficult to follow and could be shortened while still conveying the same message.
			Actually, I find the comment in Supplementary information 3 clearer, although no reference to Supplementary information 3 is made.
			Besides, as slopes of regressions in permuted networks are tightly grouped around zero (Fig. 2, thin lines indicating 
			extrema of slopes distribution overlapping each other), so type II errors do not seem to be a big problem here.
		\end{refquote}

@@

		\begin{quotation}

			This permutation approach also allows us to estimate type I and type II 
			error for our analysis. Because the permuted networks should not demonstrate any particular relationship between phylogenetic distance and partner overlap, these slopes should be similar to those obtained after permuting these networks a second time.

		\end{quotation}

	5. Suggestion to consider phylogenetic diversity instead of number of plant pairs

		\begin{refquote}
			* Testing the effect of network size on the existence of a phylogenetic signal\\
			Here, it is specifically the number of plant pairs that is studied. I wonder whether the phylogenetic diversity of plants would not be more adapted here. Is it overlooked because similar among networks?
			I think knowing more about this effect would further illuminate why the strength of the phylogenetic signal varies between networks and would be complementary to the analysis testing the effect of plant community composition.
		\end{refquote}

		\textbf{R:} We agree that phylogenetic diversity would be another option for quantifying the 'size' of these networks. However, defining the phylogenetic diversity of each network would depend strongly upon the correctness of of base tree. As we discuss in the methods, our estimates for non-angiosperms are likely to be fairly rough, and some other species are also only approximately dated. Because of this, and because this analysis would more compliment our community-composition analysis than introduce new material, we have opted no to pursue phylogenetic diversity in this manuscript. Here, we were more concerned with numbers of plant pairs since numbers of species are known to affect many areas of network structure and because the number of plant pairs is effectively the sample size for our within-network analyses.

	6. Request for consideration of multiple testing

		\begin{refquote}
			* Testing within-family existence of a phylogenetic signal\\
			Examining the strength of phylogenetic signal within plant families is an interesting idea. However, this leads to multiple testing which is prone to type I errors and I could not find mention of correction for this multiple testing in the text. There are actually high chances that there is at least one significant test in each table (1 – (1 – alpha)\^N = 0.36 and 0.91 respectively, alpha = 0.05). Yet, the authors can indicate that there are low chances to have that many significant phylogenetic signals (using the probability mass function of the Binomial distribution, see Moran 2003 in Oikos).
		\end{refquote}

		\textbf{R:} The Referee makes a very good point. We had considered these high numbers of significant slopes unlikely to occur by chance, even if we would expect one or two significant results by chance. This argument is somewhat difficult to make convincingly and briefly in the middle of the manuscript, however. Instead, we apply the sequential correlated Bonferroni test in~\citet{Drezner2016}. This development of this test was heavily motivated by the Moran paper you recommend, and we thank the Referee for pointing out this literature. We have added tables of the SCBT critical values to \emph{Supplemental Information 4} in order to provide readers with a bit more detail. We have also added a few lines to the methods to formally introduce the problem of multiple testing, some of the objections to the strict Bonferroni in~\citet{Moran2003}, and our solution to it.

@@

		Lines 355-360 now read:

		\begin{quotation}
			 In pollination networks, overlap decreased significantly with increasing phylogenetic distance in 14 of the 48 well-represented families (Table 1; Fig. 3). If we apply the correlated Bonferroni correction to account for multiple testing~\citep{Drezner2016}, all of these slopes remain significant (\emph{Supplemental Information 4}).
		\end{quotation}

		In responding to this comment, we also noted that the number of significant families in the pollination networks was incorrectly quoted in the main text. As shown in Table 1, there are actually 14 significant families in the pollination web. We have corrected this error and thank the Referee again for calling our attention to this section of the results.

	7. Suggestion to mention sampling completeness as a potential explanation for specialists

		\begin{refquote}
			On the effect of specialist pollinators\\

@@

		\begin{quotation}

			Note that some of the apparent specialists in our dataset may actually be rare species involved in more interactions which have not yet been observed~\citep{Bluthgen2006,Poisot2015}. Without information on the sampling completeness of the networks in our dataset, it is difficult to estimate the size of this effect. 
			It is possible, however, that we might observe stronger relationships between phylogenetic
			distance and niche overlap with more complete data on rare species.

		\end{quotation}

	8. Discussion of potential tradeoffs between interactions could be sharpened

		\begin{refquote}
			On plant families involved in different types of interactions\\

@@

		\begin{quotation}

			Whereas previous 
			studies have focused on the presence or absence of phylogenetic
			signal across entire networks, we take a pairwise perspective in
			order to obtain a more detailed picture of how plant phylogeny
			relates to network structure. As different plant families (which represent tractable clades for analysis) may have experienced different degrees of coevolution, convergence, etc., we also complement analyses with entire networks with comparisons among plants in the same family within a network. 
			This novel perspective allows us to investigate the relationship between phylogenetic distance and partner overlap at different scales.

		\end{quotation}

	12. Suggestion to make a figure showing distribution of webs, or at least to add countries to the list in SI

@@

	% Check. % Moran, M.D., 2003. Arguments for rejecting the sequential Bonferroni in ecological studies. Oikos, 100(2), pp.403-405.

	% Check. % Strauss, S.Y. and Whittall, J.B., 2006. Non-pollinator agents of selection on floral traits. Ecology and evolution of flowers, pp.120-138.

  \newpage

\bibliographystyle{newphy} 
\renewcommand*{\bibfont}{\raggedright}
\bibliography{manual}
